<!-- README.md is generated from README.Rmd. Please edit that file

library(rmarkdown)
render('README.Rmd', output_format=md_document())

-->
```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "##",
  fig.path = "extra/figures/README-",
  error = TRUE
)
```
# rtini - Right Triangulated Irregular Network Surface Approximation

A vectorized implementation of the Right-Triangulated Irregular Networks
(RTIN) surface approximation algorithm.  This implementation generates meshes
that are triangulated subsets of maps, subject to error tolerances.  The
vertices in the reduced mesh are vertices in the original, and they are
arranged to form right angle triangles.

The workhorse functions are `rtini_error()` and `rtini_mesh()`.  The former
computes the surface approximation error at all levels of approximation, and
the latter extract mesh triangles subject to an error tolerance.

This is package is experimental, lightly tested, and not intended for production
use.  It is unlikely this package will ever be posted on CRAN, but if you are
interested in the functionality and know of a GPL licensed home for it do let me
know.


```{r fig.width=6, fig.height=2}
library(rtini)
err <- rtini_error(volcano[1:65,1:33])
par(mfrow=c(1, 3), mai=rep(0.1, 4))
mesh <- rtini_extract(err, 2)
tris <- rbind(do.call(cbind, mesh), NA)
plot.new()
polygon(
  x=((tris - 1) %/% nrow(err)) / (ncol(err) - 1),
  y=((tris - 1) %% nrow(err)) / (nrow(err) - 1),
  col='grey90'
)
mesh <- rtini_extract(err, 10)
tris <- rbind(do.call(cbind, mesh), NA)
plot.new()
polygon(
  x=((tris - 1) %/% nrow(err)) / (ncol(err) - 1),
  y=((tris - 1) %% nrow(err)) / (nrow(err) - 1),
  col='grey90'
)
mesh <- rtini_extract(err, 30)
tris <- rbind(do.call(cbind, mesh), NA)
plot.new()
polygon(
  x=((tris - 1) %/% nrow(err)) / (ncol(err) - 1),
  y=((tris - 1) %% nrow(err)) / (nrow(err) - 1),
  col='grey90'
)
```
